Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-05-25 manuscript/manuscript.Rmd
add some text on vital rate connection to IPMs

#### Integral projection model
We use a stochastic IPM [@Rees2009] that includes the climate covariates from the vital rate statistical models. In all simulations, we ignore the random year effects so that interannual variation is driven solely by climate. We fit the random year effects in the vital rate regressions to avoid over-attributing variation to climate covariates. Our IPM follows the specification of @Chu2015 where the population of species _j_ is a density function $n(u_{j},t)$ giving the density of sized-_u_ genets at time _t_. Genet size is on the natural log scale, so that $n(u_{j},t)du$ is the number of genets whose area (on the arithmetic scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. The density function for any size _v_ at time $t+1$ is

@@

which means we are calculating growth (_G_) for individuals that survive (_S_) from time _t_ to _t+1_ and adding in newly recruited (_R_) individuals of an average sized one-year-old genet for the focal species. Our stastical model for recruitment (_R_, described above) returns the number of new recruits produced per quadrat. Following previous work [@Adler2012; @Chu2015], we assume that fecundity increases linearly with size ($R_j(v_{j},u_{j},\bar{w_{j}}) = e^{u_j}R_j(v_{j},\bar{w_{j}})$) to incorporate the recruitment function in the spatially-implicit IPM.

We used random draws from the final 1,000 iterations, thinned by 10, from each of three MCMC chains to carry-through parameter uncertainty into our population models. At each time step, we randomly selected climate covariates from one of the 14 observed years. Then, we drew the full parameter set (climate effects and density-dependence fixed effects) from a randomly selected MCMC iteration. Relatively unimportant climate covariates (those that broadly overlap 0) will have little effect on the mean of the simulation results, but can contribute to their variation. Because our focus was on the contribution of density dependence and climate covariates to population states, we set the random year effects and the random group effects to zero.

>>>>

#### Integral projection model
We use a stochastic IPM [@Rees2009] to simulate our focal populations based on the vital rate regressions described above. In all simulations, we ignore the random year effects so that interannual variation is driven solely by climate. We fit the random year effects in the vital rate regressions to avoid over-attributing variation to climate covariates. Our IPM follows the specification of @Chu2015 where the population of species _j_ is a density function $n(u_{j},t)$ giving the density of sized-_u_ genets at time _t_. Genet size is on the natural log scale, so that $n(u_{j},t)du$ is the number of genets whose area (on the arithmetic scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. The density function for any size _v_ at time $t+1$ is

@@

which means we are calculating growth (_G_) for individuals that survive (_S_) from time _t_ to _t+1_ and adding in newly recruited (_R_) individuals of an average sized one-year-old genet for the focal species. Note the _S_, _G_, and _R_ are incorporated in the IPM using the fitted vital rate regressions. Our statistical model for recruitment (_R_, described above) returns the number of new recruits produced per quadrat. Following previous work [@Adler2012; @Chu2015], we assume that fecundity increases linearly with size ($R_j(v_{j},u_{j},\bar{w_{j}}) = e^{u_j}R_j(v_{j},\bar{w_{j}})$) to incorporate the recruitment function in the spatially-implicit IPM.

We used random draws from the final 1,000 iterations, thinned by 10, from each of three MCMC chains for each vital rate regression to carry-through parameter uncertainty into our population models. At each time step, we randomly selected climate covariates from one of the 14 observed years. Then, we drew the full parameter set (climate effects and density-dependence fixed effects) from a randomly selected MCMC iteration. Relatively unimportant climate covariates (those that broadly overlap 0) will have little effect on the mean of the simulation results, but can contribute to their variation. Because our focus was on the contribution of density dependence and climate covariates to population states, we set the random year effects and the random group effects to zero.
